Model Checking Differentially Private Properties

### 2018-06-13 introduction.tex
polish

In order to illustrate applicability of our techniques, we give
detailed formalizations of several data analysis mechanisms in this
paper.
In differential privacy, data analysis mechanisms are
but randomized algorithms. We follow the standard practice in
probabilistic model checking to formalize such mechanisms
as Markov chains or Markov decision processes~\cite{Put05}. 
%We give formalizations of several differentially private mechanisms
%and explain subtle privacy conditions.
When a data analysis mechanism does not
interact with its environment, it is formalized as a Markov
chain. Otherwise, its interactions are formalized by actions in
Markov decision processes. Our formalization effectively assumes that
actions are controlled by adversaries. It is thus necessary to
consider all privacy attacks from adversaries in order to establish
differential privacy.
%\todo{What is a state?}

>>>>

In order to illustrate applicability of our techniques, we give
detailed formalizations of several data analysis mechanisms in this
paper.
In differential privacy, data analysis mechanisms are
but randomized algorithms. We follow the standard practice in
probabilistic model checking to formalize such mechanisms
as Markov chains or Markov decision processes~\cite{Put05}. 
%We give formalizations of several differentially private mechanisms
%and explain subtle privacy conditions.
When a data analysis mechanism does not
interact with its environment, it is formalized as a Markov
chain. Otherwise, its interactions are formalized by non-deterministic 
actions in
Markov decision processes. Our formalization effectively assumes that
actions are controlled by adversaries. It thus
considers all privacy attacks from adversaries in order to establish
differential privacy as required.
%\todo{What is a state?}
